\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-12 chapters/2_rel_work.tex
Update and rewrite exps. sections

This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a general framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.

>>>>

This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.

### 2019-05-12 chapters/3_algorithm.tex
Update and rewrite exps. sections

\section{Generalized framework for Signed Graph Agglomerative Clustering} \label{sec:general_framework}
This section introduces the proposed generalized framework: 
%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
we define the graph notation in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in Sec. \ref{sec:algorithm} and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in Sec. \ref{sec:alg_update_rules}.

@@

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$, in which nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

@@

\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
\begin{equation}
E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t. clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering/multicut problem} 
% w.r.t. $\mathcal{G}(V,E,\cost)$ 
corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
\begin{equation}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as measure of how balanced a clustering is.

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ of all edges connecting cluster $S_u$ to cluster $S_v$ is defined as $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} - left panel), where the choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, unsigned graphs).

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage). They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.

The Mutex Watershed \cite{wolf2018mutex}, another algorithm for signed graph partitioning, also introduces dynamical cannot-link constraints. In the supplementary material (Sec. \ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{Absolute maximum} linkage defined in Table \ref{tab:linkage-criteria} and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.

On the other hand, to our knowledge, the presented agglomerative algorithm with \emph{Average}, \emph{Max} or \emph{Min} linkage was never applied to signed graphs or combined with cannot-link constraints, \UPDATE{thus we decided to test all these new variations.}

Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
\cite{nunez2013machine} for example proposed a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction. In the next chapters, our experiments focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most used ones.

>>>>

\section{Generalized framework for Signed Graph Agglomerative Clustering} \label{sec:general_framework}
In this section, we first define the graph notation (Sec.~\ref{sec:notation}) and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec. \ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec. \ref{sec:alg_update_rules}).
 % introduces the proposed generalized framework: 
%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
% we  in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in  and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in .

@@

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes, in which nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $\,S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

@@

\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
\begin{equation}
E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t. clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering/multicut problem} 
% w.r.t. $\mathcal{G}(V,E,\cost)$ 
corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
\begin{equation}\label{eq:multicut_obj}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as measure of how balanced a clustering is.

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage). They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints. In Appendix \ref{sec:equivalence_MWS} we prove that it can be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def. in Table \ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
\UPDATE{Less-known options: \emph{Average}, \emph{Max} or \emph{Min} linkage applied to signed graphs or never combined with cannot-link constraints.}

Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
\cite{nunez2013machine} for example uses a learned approach where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction. In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

### 2019-05-12 chapters/5_experiments_cityscapes.tex
Update exp. sec. and NeurIPS 2019
Update and rewrite exps. sections

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}
A successful proposal-free method was recently presented in \cite{liu2018affinity} and a setup equivalent to the one described in Sec. \ref{sec:grid_graph} but uses a more complex pipeline to select region of interests in the image, predict semantic pixel information that is used to improve pixel affinities, etc... We used exactly their code and pipeline, but we replaced their final agglomeration clustering step with the algorithms proposed in this paper...

In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...

I should mention the main trick in the loss: ignore background pixels (so focus on boundaries!)

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. For our experiments, we used the state-of-the-art proposal-free pipeline proposed in \cite{liu2018affinity} (GMIS) that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}. See Appendix \ref{sec:cityscapes_appendix} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 in \cite{liu2018affinity}.

### 2019-05-12 chapters/5_experiments_compare_rules.tex
Update and rewrite exps. sections

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
\caption{\algname{} with different linkage criteria on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data. Red arrows point to wrongly split regions. Yellow arrows point out merge errors. Green arrows indicate challenging, but correctly segmented regions. 
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}
\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand\\Score} & VI-Score \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
DTWS + LMC \cite{beier2016efficient}& -& & \\
DTWS + avgHC &-& & \\
DTWS  & -& & \\
THRESH &-& & \\ \hline
\algname{} & Average& & \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & & \\
GAEC \cite{keuper2015efficient} & Sum & & \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr.  & & \\
        \end{tabular}
    \captionof{table}{Arand-Scores and VI-Scores on CREMI challenge training data}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{\UPDATE{TBD:} Scores on test data}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

\subsection{CREMI Challenge} \label{sec:exp_first_comparison}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}. The data is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds.

\textbf{Training } We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}. We further simulated low contrast sections... and missing sections by setting their intensity value to zero... We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).

\textbf{Additional methods tested }  We compare the performances of the algorithms in our framework with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As baseline methods, we consider a simple thresholding (THRESH) and a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). For these baselines, affinities are converted to a boundary map \UPDATE{by taking a weighted average over short- and long-range edge connections}. Other state-of-the-art neuron-segmentation multi-step-pipelines first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.

\textbf{Comparison results } Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}
(see Table \ref{tab:results_cremi_train}). This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters. The performances of all linkage criteria listed in Table \ref{tab:linkage-criteria} are summarized in Table \ref{tab:cremi_train_full} in Appendix and in Fig. \ref{fig:cremi_comparison}, where we highlight some of the major mistakes...

>>>>

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data. Only the few wrongly segmented regions are highlighted in colors. Red arrows point to wrongly split regions. Yellow arrows point out merge errors. Green arrows indicate challenging, but correctly segmented regions. 
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}
\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand} & \makecell{VI-Merge} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
DTWS + LMC \cite{beier2016efficient}& -& & \\
DTWS + avgHC &-& & \\
DTWS  & -& & \\
THRESH &-& & \\ \hline
\algname{} & Average& 0.936 & 0.685 \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 & 0.642 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 & 0.714 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 & 0.539 \\
        \end{tabular}
    \captionof{table}{Arand-Scores and VI-Scores on CREMI challenge training data}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{\UPDATE{TBD:} Scores on test data}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

\subsection{CREMI Challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}. The data is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds.

\textbf{Training details} \UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}. We further simulated low contrast sections... and missing sections by setting their intensity value to zero... We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).}

\textbf{Additional methods tested }  We compare the performances of the algorithms in our framework with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As baseline methods, we consider a simple thresholding (THRESH) and a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). For these baselines, affinities are converted to a boundary map \UPDATE{by taking a weighted average over short- and long-range edge connections}. Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.

### 2019-05-12 chapters/5_experiments_intro.tex
Update and rewrite exps. sections

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. While a lot of progress is being made, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}.
\TODO{subsections description}

\subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN. 
Thus, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
In the Supplementary material (Sec. \ref{sec:training_details}) we provide more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence. In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}. The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
\begin{equation} \label{eq:mappings}
\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) + \log \left( \frac{\beta}{1-\beta} \right),
\end{equation}
where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation. We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage. \TODO{Comment about HC threshold}

>>>>

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
In Sec. \ref{sec:grid_graph}, we present how we predicted signed edge weights with a CNN. Then we introduce the CREMI challenge and our tested methods in Sec. \ref{sec:cremi_challenge} and present our results in Sec. \ref{sec:comparison_exps}.

\subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN. 
Thus, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence. In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}. The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
\begin{equation} \label{eq:mappings}
\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) + \log \left( \frac{\beta}{1-\beta} \right),
\end{equation}
where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation. We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage. \TODO{HC threshold}
